RCloud: Integrating Exploratory Visualization, Analysis and Deployment

### 2014-03-27 discussion.tex
yes

Experience with deploying RCloud in a community of data analysts
has provided some insight into how well the proposed requirements
were met and were appropriate to the tasks in their work.
This experience may be informative to researchers and designers
of future systems supporting collaborative visual analytics.

Returning to the design considerations defined by Heer and Agrawala,
our experience underscores the value of many of their proposals,
and indicates areas for further exploration.

{\bf Shared artifacts and artifact histories} are a central feature
of RCloud. The prototype aimed at making it convenient to collaborate
on experimental workbooks and the analyses that result. We observed
that analysts readily shared ideas through RCloud. 
creating experiments
in workbooks and sharing URLs to discuss analysis and programming
problems, instead of sending screenshots in PowerPoint.\todo{Talk about artifact histories?}

>>>>

Experience with deploying RCloud in a community of data analysts
has provided some insight about how the proposed requirements
were met, and to what extent they were appropriate.
This experience may be informative to researchers and designers
of future systems supporting collaborative visual analytics.

Returning to the design considerations defined by Heer and Agrawala,
our experience underscores the importance of many of their proposals,
and indicates areas for further exploration.

{\bf Shared artifacts and artifact histories} are a central feature
of RCloud. The prototype aimed at making it convenient to collaborate
on experimental workbooks and the analyses that result. We observed
that analysts readily shared ideas through RCloud. They used RCloud
to discuss data analysis, programming problems, and to publish results
by sharing URLs instead of instead of embedding screenshots in
PowerPoint.\todo{Talk about artifact histories?}

### 2014-03-27 relatedwork.tex
yes

The need for integrating statistics and visualization has been
highlighted in previous studies and is widely understood by
various technical communities \cite{Perer:2008:ISA}

@@

One overall goal is to reduce the gap between implementers and deployers
of technology. Don't want a team of 20 IT people to support 5 data scientists.

% devops for data science.

>>>>

The need for integrating statistics and visualization has been
highlighted in previous studies and is widely understood by
various technical communities \cite{Perer:2008:ISA}
Lucas and Roth were early advocates of combining
data exploration with presentation and publication \cite{Lucas:1996:EIV}.

@@

One overall goal is to reduce the gap between implementers and deployers
of technology in visual analytics. The fusion of development with production
operations in software release management ("devops" \cite{Httermann:2012:DD}) is a trend in web services and related fields. There is certainly an economic
benefit to making it possible for data scientists to expend a little more
effort in creating experiments, to eliminate the need for a programming
team to recreate their results in production.
